---
title: "Analyses"
author: "Matt Blanchard"
date: "05/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,
                      echo=FALSE, # set to FALSE to remove the code output
                      warning=FALSE, 
                      message=FALSE)

```

## Load packages and read the cleaned data
``` {r read}
library(tidyverse)
library(GGally)
library(naniar)
library(corrplot)

# set the working directory
# setwd("/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/")

# read in the individual-level dataset
d.uid <- read_csv("/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/data/190507_uid_data.csv")

# read in the dyad-level dataset
d.grp <- read_csv("/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/data/190507_dyad_data.csv")
```

## Explore the data
```{r explore}
# create df of numeric variable names
# individual-level data
numeric_vars_uid <- d.uid %>% 
  select_if(is.numeric) %>% 
  select(-member) %>% 
  names

# dyad-level data
numeric_vars_grp <- d.grp %>% 
  select_if(is.numeric) %>% 
  names

```


## Calculate number of missing values for each variable
All looks ok. There are a few things to note:
* High number of scores missing for some DPA variables in both the individual- and dyad-level datasets because participants did not engage in some of these pattern of behaviour. For example, recklessness on mdmt and crt are missing because groups obtained 100% accuracy so there was no opportunity to be reckless. 
* High number of scores missing for adaptability, risk aversion and trust missing because they were added to the protocol part way through testing.
* Some R2F values missing because some participants skipped this measure to get out on time (~ 12 individuals or ~ 6 groups).
```{r}
# individual-level data
# high number missing for some DPA variables because participants did not engage in this pattern of behaviour (not because data is actually missing)
# For example, recklessness on mdmt and crt because groups obtained 100% accuracy so there was no opportunity to be reckless
# adaptability, risk aversion and trust missing because they were added to the protocol part way through testing
colSums(sapply(d.uid, is.na)) %>% 
  as.data.frame() %>% 
  rename(Missing = ".") %>% 
  tibble::rownames_to_column() %>% 
  filter(!rowname %in% c("issue_note_2", "issue_note_1", "issue")) %>% 
  arrange(desc(Missing))

# dyad-level data
# high number missing for some DPA variables because participants did not engage in this pattern of behaviour (not because data is actually missing)
# For example, recklessness on mdmt, crt and adr because groups obtained 100% accuracy so there was no opportunity to be reckless
# adaptability, risk aversion and trust missing because they were added to the protocol part way through testing
colSums(sapply(d.grp, is.na)) %>% 
  as.data.frame() %>% 
  rename(Missing = ".") %>% 
  tibble::rownames_to_column() %>% 
  filter(!rowname %in% c("issue_note_2", "issue_note_1", "issue")) %>% 
  arrange(desc(Missing))
```


## Plot the number of missing values for each variable
```{r}
gg_miss_var(d.uid %>% select(-issue_note_2, -issue_note_1, -issue))
gg_miss_var(d.grp %>% select(-issue_note_2, -issue_note_1, -issue))
```

## An alternative method of plotting missing values
```{r}
gg_miss_upset(d.uid %>% select(-issue_note_2, -issue_note_1, -issue))
gg_miss_upset(d.grp %>% select(-issue_note_2, -issue_note_1, -issue))
```

## Create separate distribution and scatter plots for each variable using GGally package
# Raven's Advanced Progressive Matrices
Individual accuracy is (1) positively correlated with confidence, decisiveness, competence and optimality; and (2) negatively correlated with hesitency
Individual confidence is (1) positively correlated with decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
The same relationships occurred for groups. Although, the relationship between confidence and recklessness was weaker

Competence and optimality were perfectly correlated (+1) - check calculation

# Medical Decision Making Test
Individual accuracy is (1) positively correlated with confidence, decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
Individual confidence is (1) positively correlated with decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
The same relationships occurred for groups with the exception that accuracy did not relate to recklessness. Also, the relationship between confidence and recklessness was weaker

# General Knowledge Test
Individual accuracy is positively correlated with competence and optimality only
Individual confidence is (1) positively correlated with decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
The same relationships occurred for groups

# Cognitive Reflection Test
Individual accuracy is (1) positively correlated with confidence, decisiveness, competence and optimality; and (2) negatively correlated with hesitency
Individual confidence is (1) positively correlated with decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
The same relationships occurred for groups

# Applying Decision Rules
Individual accuracy is (1) positively correlated with confidence, decisiveness, competence and optimality; and (2) negatively correlated with hesitency
Individual confidence is (1) positively correlated with decisiveness, recklessness, competence and optimality; and (2) negatively correlated with hesitency
The same relationships occurred for groups with the exception that accuracy also related to recklessness

# Resistance to Framing
Individuals that had a larger framing effect also had a larger framing effect when working in a group

# Accuracy
For both individuals and groups there is a positive manifold for accuracy across tests except GK doesn't correlate with the others

# Confidence
For both individuals and groups there was a positive manifold for confidence across tests

# Decisiveness
For individuals and groups, there is a positive manifold for decisiveness across tests except MDMT doesn't correlate with the others. 

# Recklessness
For individuals, recklessness only positively correlates between GK, CRT and ADR. No relationship for RAPM and MDMT with any of the tests.
For groups, recklessness only positively correlates between RAPM, GK, CRT and ADR. No relationship for MDMT with any of the tests.

# Competence
For individuals and groups, there was a positive manifold for Competence across tests with the exception of GK (no relationship)

# Hesitancy
For individuals and groups, there was a positive manifold for Hesitancy across tests with the exception of MDMT (no relationship)

# Other variables
Trust positively correlates with adaptability (both sub-factors and the global factor)
The cognitive facet of Adaptability positively correlates with Agreeableness and Intellect
The affective facet of Adaptability positively correlates with Extraversion and negatively with Neuroticism

```{r}
# library(GGally)

# RAPM
plot <- d.uid %>% 
ggpairs(columns = numeric_vars_uid[c(1:14)],
        title = "RAPM")

ggsave(plot, "/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/output/ggpairs_rapm.png", width = 16, height = 10)

# MDMT
d %>% 
ggpairs(columns = numeric_vars_uid[c(15:28)],
        title = "MDMT",
        ggsave("/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/output/ggpairs_mdmt.png", width = 16, height = 10))

# GK
d %>% 
ggpairs(columns = numeric_vars_uid[c(29, 31, 33, 35, 37, 39, 41, 30, 32, 34, 36, 38, 40, 42)],
        title = "GK",
        ggsave("/Users/blattymanchard/Dropbox (Sydney Uni)/R_projects/S2_CI/output/ggpairs_gk.png", width = 16 + 2), height = 10))

# ADR
d %>% 
ggpairs(columns = numeric_vars_uid[c(57, 59, 61, 63, 65, 67, 69, 58, 60, 62, 64, 66, 68, 70)],
        title = "ADR")

# R2F
d %>% 
  ggpairs(columns = numeric_vars_uid[c(71:72)],
          title = "R2F")

# Accuracy
d %>% 
  ggpairs(columns = numeric_vars_uid[c(1, 15, 29, 43, 57, 8, 22, 30, 44, 58)],
          title = "Accuracy")

# Confidence
d %>% 
  ggpairs(columns = numeric_vars_uid[c(2, 16, 31, 45, 59, 9, 23, 32, 46, 60)],
          title = "Confidence")

# Decisiveness
d %>% 
  ggpairs(columns = numeric_vars_uid[c(3, 17, 33, 47, 61, 10, 24, 34, 48, 62)],
          title = "Decisiveness")

# Recklessness
d %>% 
  ggpairs(columns = numeric_vars_uid[c(4, 18, 35, 49, 63, 11, 25, 36, 50, 64)],
          title = "Recklessness")

# Competence
d %>% 
  ggpairs(columns = numeric_vars_uid[c(5, 19, 37, 51, 65, 12, 26, 38, 52, 66)],
          title = "Competence")

# Optimality
# d %>% 
#   ggpairs(columns = numeric_vars[c(6, 20, 39, 53, 67, 13, 27, 40, 54, 68)],
#           title = "Optimality")

# Hesitancy
d %>% 
  ggpairs(columns = numeric_vars[c(7, 21, 41, 55, 69, 14, 28, 42, 56, 70)],
          title = "Hesitancy")

# Other variables
d %>% 
  ggpairs(columns = numeric_vars[c(73:86)],
          title = "Other variables")
```


## Let's plot the correlations between all of the variables in the dataset
```{r}
d_cor <- cor(d[,numeric_vars],
                      use = "pairwise.complete.obs")

cp <- corrplot(d_cor,
               order = "hclust",
               method = "square",
               tl.col = "black")
```




